\documentclass{article}

\title{Problem Set 1}
\author{Sam Hunt}
\date{January 2025}

\begin{document}

\maketitle
\section{Introduction}
My interest in data science and economics primarily comes from my interest in academic research, which takes a lot of data science skill to perform effectively. My interests are in government policy, and I would like to one day do research that is influential in public policy debates. Currently, I am taking a section of honors research with Dr. Huynh, and so I would like to incorporate my final project for this class into that research so that I may have a very well-done thesis for the purpose of applying to grad school. That honors thesis is generally about using econometrics to measure the impacts of tariffs or trade war, however, I do not yet have a clearly defined thesis. My goal from this class is not necessarily to come out of it an A+ coder, but at least learn the baseline systems and skills so that I am competent enough to practice and get better on my own in the future. Graduation has sneaked up on me, as I will be eligible to graduate in May of 2026, but I don't have a complete idea of what I am going to do. I might be applying to PhD programs or I might try to get some research job or internship right away. Sometimes it feels like I will not be able to get either, so who knows what I will do then! However, regardless of where I end up, I know that I will continue learning and doing as much research as I can.
\section{Equation}

\[a^2+b^2=c^2\]
\end{document}